---
title: "Houston_Ground_Truth"
author: "Andrew Maloney"
date: "9/4/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
# Loading Packages
library(dplyr)
library(bulletxtrctr)
library(x3ptools)
library(ggplot2)
library(readr)
library(purrr)
library(stringr)
library(tidyr)


```

## Determine ground truth for lands and bullets

### Step One

- bullets from the same barrel are matches, bullets from different barrels are not matches. In case one of the bullets is unknown, we do not know whether there is a match or not.

- Lands from the same bullet are matches if they are the same.  In case the lands are on bullets from different barrels they are not matches

Not known yet: 

-Matches between questioned and known bullets
-Matches between questioned and other questioned bullets
- Same lands between different bullets from the same barrel 
-same lands between any questioned bullets with any other bullet

```{r}
# Determining Ground Truth 

features_1 <- comparisons_1 %>% select(-cms2_per_mm, -cms_per_mm, -lag_mm, -length_mm, -matches_per_mm, -mismatches_per_mm, -non_cms_per_mm, -rfscore)

features_1 <- features_1 %>% mutate(
  samesource = ifelse(BarrelA==BarrelB & BulletA == BulletB, LandA==LandB, NA),
  samebarrel = BarrelA == BarrelB,
  samebarrel = ifelse((BarrelA == "Unknowns" | BarrelB == "Unknowns") & (BulletA != BulletB), NA, samebarrel),
  samesource = ifelse(!samebarrel, FALSE, samesource)
  )


features_1 <- features_1 %>% mutate(comparison = paste0(pmin(Bullet1, Bullet2)," vs ", pmax(Bullet1, Bullet2)))

head(features_1)

#samesource = 1/6 between Barrel-Bullet-Land Scores
#samebarrel = Same Barrels when being compared
#comparison = Comparisons of Barrel-Bullet-Land

#-----------------------------------------------------------------------------------------------

features_2 <- comparisons_2 %>% select(-cms2_per_mm, -cms_per_mm, -lag_mm, -length_mm, -matches_per_mm, -mismatches_per_mm, -non_cms_per_mm, -rfscore)

features_2 <- features_2 %>% mutate(
  samesource = ifelse(BarrelA==BarrelB & BulletA == BulletB, LandA==LandB, NA),
  samebarrel = BarrelA == BarrelB,
  samebarrel = ifelse((BarrelA == "Unknowns" | BarrelB == "Unknowns") & (BulletA != BulletB), NA, samebarrel),
  samesource = ifelse(!samebarrel, FALSE, samesource)
  )


features_2 <- features_2 %>% mutate(comparison = paste0(pmin(Bullet1, Bullet2)," vs ", pmax(Bullet1, Bullet2)))

head(features_2)

#-------------------------------------------------------------------------------------------------


features_3 <- comparisons_3 %>% select(-cms2_per_mm, -cms_per_mm, -lag_mm, -length_mm, -matches_per_mm, -mismatches_per_mm, -non_cms_per_mm, -rfscore)

features_3 <- features_3 %>% mutate(
  samesource = ifelse(BarrelA==BarrelB & BulletA == BulletB, LandA==LandB, NA),
  samebarrel = BarrelA == BarrelB,
  samebarrel = ifelse((BarrelA == "Unknowns" | BarrelB == "Unknowns") & (BulletA != BulletB), NA, samebarrel),
  samesource = ifelse(!samebarrel, FALSE, samesource)
  )


features_3 <- features_3 %>% mutate(comparison = paste0(pmin(Bullet1, Bullet2)," vs ", pmax(Bullet1, Bullet2)))

head(features_3)
```


### Step Two 

Calculate: 
- "bestlandmatch" is using SAM scores to determine which lands match the best between any two bullets

- "sameland_pred" is calculated for all bullets to check if the SAM score is significantly higher than the non-matching lands (based on a bootstrap)

- "samebarrel_pred" is the maximum for each bullet to bullet comparison

```{r}


f2nest_1 <- features_1 %>% 
#  filter(!(barrel1==barrel2 & bullet1 == bullet2)) %>% 
  group_by(BarrelA, BulletA, BarrelB, BulletB) %>%  nest()  


f3nest_1 <- f2nest_1 %>% mutate(
  sam_ccf = data %>% purrr::map_dbl(.f=function(d) 
    max(bulletxtrctr::compute_average_scores(d$LandA, d$LandB, d$ccf, addNA = TRUE)))
  )



f3nest_1 <- f3nest_1 %>% mutate(
  data = data %>% purrr::map(.f=function(d) {
    d$bestlandmatch = bulletxtrctr::bullet_to_land_predict(d$LandA, d$LandB, d$ccf, difference=-1, alpha = 1, addNA = FALSE)    
    d
  })
  )


f3nest_1 <- f3nest_1 %>% mutate(
  data = data %>% purrr::map(.f=function(d) {
    d$sameland_pred = bulletxtrctr::bullet_to_land_predict(d$LandA, d$LandB, d$ccf, difference=0.1, alpha = 0.05, addNA = FALSE)    
    d
  })
  )

f3nest_1 <- f3nest_1 %>% mutate(
  samebarrel_pred = data %>% purrr::map_dbl(.f=function(d) 
    max(d$sameland_pred))
  )


#--------------------------------------------------------------------------------



f2nest_2 <- features_2 %>% 
#  filter(!(barrel1==barrel2 & bullet1 == bullet2)) %>% 
  group_by(BarrelA, BulletA, BarrelB, BulletB) %>%  nest()  


f3nest_2 <- f2nest_2 %>% mutate(
  sam_ccf = data %>% purrr::map_dbl(.f=function(d) 
    max(bulletxtrctr::compute_average_scores(d$LandA, d$LandB, d$ccf, addNA = TRUE)))
  )



f3nest_2 <- f3nest_2 %>% mutate(
  data = data %>% purrr::map(.f=function(d) {
    d$bestlandmatch = bulletxtrctr::bullet_to_land_predict(d$LandA, d$LandB, d$ccf, difference=-1, alpha = 1, addNA = FALSE)    
    d
  })
  )


f3nest_2 <- f3nest_2 %>% mutate(
  data = data %>% purrr::map(.f=function(d) {
    d$sameland_pred = bulletxtrctr::bullet_to_land_predict(d$LandA, d$LandB, d$ccf, difference=0.1, alpha = 0.05, addNA = FALSE)    
    d
  })
  )

f3nest_2 <- f3nest_2 %>% mutate(
  samebarrel_pred = data %>% purrr::map_dbl(.f=function(d) 
    max(d$sameland_pred))
  )

#--------------------------------------------------------------------------------

f2nest_3 <- features_3 %>% 
#  filter(!(barrel1==barrel2 & bullet1 == bullet2)) %>% 
  group_by(BarrelA, BulletA, BarrelB, BulletB) %>%  nest()  


f3nest_3 <- f2nest_3 %>% mutate(
  sam_ccf = data %>% purrr::map_dbl(.f=function(d) 
    max(bulletxtrctr::compute_average_scores(d$LandA, d$LandB, d$ccf, addNA = TRUE)))
  )



f3nest_3 <- f3nest_3 %>% mutate(
  data = data %>% purrr::map(.f=function(d) {
    d$bestlandmatch = bulletxtrctr::bullet_to_land_predict(d$LandA, d$LandB, d$ccf, difference=-1, alpha = 1, addNA = FALSE)    
    d
  })
  )


f3nest_3 <- f3nest_3 %>% mutate(
  data = data %>% purrr::map(.f=function(d) {
    d$sameland_pred = bulletxtrctr::bullet_to_land_predict(d$LandA, d$LandB, d$ccf, difference=0.1, alpha = 0.05, addNA = FALSE)    
    d
  })
  )

f3nest_3 <- f3nest_3 %>% mutate(
  samebarrel_pred = data %>% purrr::map_dbl(.f=function(d) 
    max(d$sameland_pred))
  )


```



Check Predictions 

- Use "bestlandmatch" to identify matching lands between different bullets from the same barrel


```{r}

f3long_1 <- f3nest_1 %>% filter(BarrelA==BarrelB, BulletA!=BulletB, BarrelA != "Unknowns") %>%
  unnest(data) 

f3long_1 %>%
  ggplot(aes(x = LandA, y = LandB, fill=ccf)) +
  geom_tile() +
  facet_wrap(~BarrelA+BulletA+BulletB) +
  scale_fill_gradient2(low="darkgrey", high="darkorange", midpoint=.5) +
  scale_colour_manual(values="darkorange") +
  geom_point(colour="red", data = f3long_1 %>% filter(bestlandmatch))+
  ggtitle("Houston_Group_1")


#---------------------------------------------------------------------

f3long_2 <- f3nest_2 %>% filter(BarrelA==BarrelB, BulletA!=BulletB, BarrelA != "Unknowns") %>%
  unnest(data) 
f3long_2 %>%
  ggplot(aes(x = LandA, y = LandB, fill=ccf)) +
  geom_tile() +
  facet_wrap(~BarrelA+BulletA+BulletB) +
  scale_fill_gradient2(low="darkgrey", high="darkorange", midpoint=.5) +
  scale_colour_manual(values="darkorange") +
  geom_point(colour="red", data = f3long_2 %>% filter(bestlandmatch))+
  ggtitle("Houston_Group_2")

#--------------------------------------------------------------------

f3long_3 <- f3nest_3 %>% filter(BarrelA==BarrelB, BulletA!=BulletB, BarrelA != "Unknowns") %>%
  unnest(data) 
f3long_3 %>%
  ggplot(aes(x = LandA, y = LandB, fill=ccf)) +
  geom_tile() +
  facet_wrap(~BarrelA+BulletA+BulletB) +
  scale_fill_gradient2(low="darkgrey", high="darkorange", midpoint=.5) +
  scale_colour_manual(values="darkorange") +
  geom_point(colour="red", data = f3long_3 %>% filter(bestlandmatch))+
  ggtitle("Houston_Group_3")


```

```{r}


features_1 <- f3nest_1 %>% unnest(data)

features_1 <- features_1 %>% mutate(
  samesource = ifelse(BarrelA==BarrelB & BulletA!=BulletB & BarrelA != "Unknown", bestlandmatch, samesource)
)


table(features_1$samesource)

f3nest_1 <- features_1 %>% 
#  filter(!(barrel1==barrel2 & bullet1 == bullet2)) %>% 
  group_by(comparison,BarrelA, BulletA, BarrelB, BulletB, samebarrel, samebarrel_pred,
           sam_ccf, Bullet1, Bullet2) %>%  nest() 




#---------------------------------------------------------------------------------------------

features_2 <- f3nest_2 %>% unnest(data)

features_2 <- features_2 %>% mutate(
  samesource = ifelse(BarrelA==BarrelB & BulletA!=BulletB & BarrelA != "Unknown", bestlandmatch, samesource)
)


table(features_2$samesource)

f3nest_2 <- features_2 %>% 
#  filter(!(barrel1==barrel2 & bullet1 == bullet2)) %>% 
  group_by(comparison,BarrelA, BulletA, BarrelB, BulletB, samebarrel, samebarrel_pred,
           sam_ccf, Bullet1, Bullet2) %>%  nest() 


#--------------------------------------------------------------------------------------------------

features_3 <- f3nest_3 %>% unnest(data)

features_3 <- features_3 %>% mutate(
  samesource = ifelse(BarrelA==BarrelB & BulletA!=BulletB & BarrelA != "Unknown", bestlandmatch, samesource)
)


table(features_3$samesource)

f3nest_3 <- features_3 %>% 
#  filter(!(barrel1==barrel2 & bullet1 == bullet2)) %>% 
  group_by(comparison,BarrelA, BulletA, BarrelB, BulletB, samebarrel, samebarrel_pred,
           sam_ccf, Bullet1, Bullet2) %>%  nest() 


```

```{r}

f3nest_1 <- f3nest_1 %>% mutate(
  truth = c("different-source", "same-source")[samebarrel+1],
  truth = ifelse(is.na(samebarrel), "Unknown", truth),
  prediction = c("different-source", "same-source")[samebarrel_pred+1]
) 


f3nest_1 %>% group_by(comparison) %>%
  summarise(sam_ccf = mean(sam_ccf),
            truth = truth[1],
            prediction = prediction[1]) %>% 
  ggplot(aes(x = sam_ccf, y = truth, colour = prediction)) + geom_jitter() +
  theme_bw() +
  scale_colour_manual(values=c("darkgrey", "darkorange"))+
  ggtitle("Houston_Group_1")

#----------------------------------------------------------

f3nest_2 <- f3nest_2 %>% mutate(
  truth = c("different-source", "same-source")[samebarrel+1],
  truth = ifelse(is.na(samebarrel), "Unknown", truth),
  prediction = c("different-source", "same-source")[samebarrel_pred+1]
) 


f3nest_2 %>% group_by(comparison) %>%
  summarise(sam_ccf = mean(sam_ccf),
            truth = truth[1],
            prediction = prediction[1]) %>% 
  ggplot(aes(x = sam_ccf, y = truth, colour = prediction)) + geom_jitter() +
  theme_bw() +
  scale_colour_manual(values=c("darkgrey", "darkorange"))+
  ggtitle("Houston_Group_2")


#-----------------------------------------------------------------------------

f3nest_3 <- f3nest_3 %>% mutate(
  truth = c("different-source", "same-source")[samebarrel+1],
  truth = ifelse(is.na(samebarrel), "Unknown", truth),
  prediction = c("different-source", "same-source")[samebarrel_pred+1]
) 


f3nest_3 %>% group_by(comparison) %>%
  summarise(sam_ccf = mean(sam_ccf),
            truth = truth[1],
            prediction = prediction[1]) %>% 
  ggplot(aes(x = sam_ccf, y = truth, colour = prediction)) + geom_jitter() +
  theme_bw() +
  scale_colour_manual(values=c("darkgrey", "darkorange"))+
  ggtitle("Houston_Group_3")




```

```{r}
#Same Plot as above but a condensed facet 

f3long_1 %>%
  ggplot(aes(x = LandA, y = LandB, fill=ccf)) +
  geom_tile() +
  facet_wrap(~BarrelA) +
  scale_fill_gradient2(low="darkgrey", high="darkorange", midpoint=.5) +
  geom_point(colour="red", data = f3long_1 %>% filter(sameland_pred)) 

f3long_2 %>%
  ggplot(aes(x = LandA, y = LandB, fill=ccf)) +
  geom_tile() +
  facet_wrap(~BarrelA) +
  scale_fill_gradient2(low="darkgrey", high="darkorange", midpoint=.5) +
  geom_point(colour="red", data = f3long_2 %>% filter(sameland_pred)) 

f3long_3 %>%
  ggplot(aes(x = LandA, y = LandB, fill=ccf)) +
  geom_tile() +
  facet_wrap(~BarrelA) +
  scale_fill_gradient2(low="darkgrey", high="darkorange", midpoint=.5) +
  geom_point(colour="red", data = f3long_3 %>% filter(sameland_pred)) 





```

```{r}
f3nest_1 %>% filter(truth =="different-source" & prediction=="same-source")

f3nest_2 %>% filter(truth =="different-source" & prediction=="same-source")

f3nest_3 %>% filter(truth =="different-source" & prediction=="same-source")


```

```{r}

table(f3nest_1$BulletA)


questioned_1 <- f3nest_1 %>% filter(BarrelB == "Unknowns")





questioned_1 %>%
  ggplot(aes(x = BulletA, y = BulletB, fill=sam_ccf)) + 
  geom_tile(data = questioned_1) +
  scale_fill_gradient2(low="darkgrey", high="darkorange1", midpoint=.5) +
  scale_colour_manual(values=c("darkorange")) +
  facet_grid(.~BarrelA, space = "free", scales="free") +
  theme_bw() +
  geom_tile(colour = "black", size=1)+
  geom_point(colour = "red", data = questioned_1 %>% filter(samebarrel_pred==1))+
  ggtitle("Houston_Group_1")




```

```{r}


table(f3nest_2$BulletA)


questioned_2 <- f3nest_2 %>% filter(BarrelB == "Unknowns")

questioned_2 <- questioned_2 %>%
  ungroup(BarrelA) %>%
  mutate(
    BarrelA = factor(factor(BarrelA), levels = c("KC", "KD", "KE", "KF", "KG", "Unknowns")),
    BulletB = factor(BulletB, levels = rev(c("U23", "U34", "U41", "U61", "U63", "U66", "U73", "U98"))),
    BulletA = factor(BulletA, levels = c("1", "2", "3", rev(levels(BulletB))))
  ) 



questioned_2 %>%
  ggplot(aes(x = BulletA, y = BulletB, fill=sam_ccf)) + 
  geom_tile(data = questioned_2) +
  scale_fill_gradient2(low="darkgrey", high="darkorange1", midpoint=.5) +
  scale_colour_manual(values=c("darkorange")) +
  facet_grid(.~BarrelA, space = "free", scales="free") +
  theme_bw() +
  geom_tile(colour = "black", size=1)+
  geom_point(colour = "red", data = questioned_2 %>% filter(samebarrel_pred==1))+
  ggtitle("Houston_Group_2")

```

```{r}


table(f3nest_3$BarrelA)


questioned_3 <- f3nest_3 %>% filter(BarrelB == "Unknowns")

questioned_3 <- questioned_3 %>%
  ungroup(BarrelA) %>%
  mutate(
    BarrelA = factor(factor(BarrelA), levels = c("KF", "KG", "KH", "KI", "KJ", "Unknowns")),
    BulletB = factor(BulletB, levels = rev(c("U14", "U27", "U33", "U36", "U45", "U49", "U56", "U65"))),
    BulletA = factor(BulletA, levels = c("1", "2", "3", rev(levels(BulletB))))
  ) 



questioned_3 %>%
  ggplot(aes(x = BulletA, y = BulletB, fill=sam_ccf)) + 
  geom_tile(data = questioned_3) +
  scale_fill_gradient2(low="darkgrey", high="darkorange1", midpoint=.5) +
  scale_colour_manual(values=c("darkorange")) +
  facet_grid(.~BarrelA, space = "free", scales="free") +
  theme_bw() +
  geom_tile(colour = "black", size=1)+
  geom_point(colour = "red", data = questioned_3 %>% filter(samebarrel_pred==1))+
  ggtitle("Houston_Group_3")







```


```{r}


f2_1 <- f3nest_1 %>% unnest(data)
f2_1 <- f2_1 %>% mutate(
  samesource = ifelse(is.na(samesource) & !samebarrel, FALSE, samesource),
  samesource = ifelse(is.na(samesource) & samebarrel, bestlandmatch, samesource)
)

```

```{r}
f2_2 <- f3nest_2 %>% unnest(data)
f2_2 <- f2_2 %>% mutate(
  samesource = ifelse(is.na(samesource) & !samebarrel, FALSE, samesource),
  samesource = ifelse(is.na(samesource) & samebarrel, bestlandmatch, samesource)
)

```

```{r}
f2_3 <- f3nest_3 %>% unnest(data)
f2_3 <- f2_3 %>% mutate(
  samesource = ifelse(is.na(samesource) & !samebarrel, FALSE, samesource),
  samesource = ifelse(is.na(samesource) & samebarrel, bestlandmatch, samesource)
)

```


```{r}
questioned_1 <- f2_1 %>% filter(BarrelB == "Unknowns")

questioned_1 <- questioned_1 %>%
  ungroup(BarrelA) %>%
  mutate(
    BarrelA = factor(factor(BarrelA), levels = c("KA", "KB", "KC", "KD", "KE", "Unknowns")),
    BulletB = factor(BulletB, levels = rev(c("U10", "U15", "U28", "U36", "U37", "U40", "U42", "U77"))),
    BulletA = factor(BulletA, levels = c("1", "2", "3", rev(levels(BulletB))))
  ) 

```


```{r}

questioned_2 <- f2_2 %>% filter(BarrelB == "Unknowns")

questioned_2 <- questioned_2 %>%
  ungroup(BarrelA) %>%
  mutate(
    BarrelA = factor(factor(BarrelA), levels = c("KC", "KD", "KE", "KF", "KG", "Unknowns")),
    BulletB = factor(BulletB, levels = rev(c("U23", "U34", "U41", "U61", "U63", "U66", "U73", "U98"))),
    BulletA = factor(BulletA, levels = c("1", "2", "3", rev(levels(BulletB))))
  ) 

```


```{r}
questioned_3 <- f2_3 %>% filter(BarrelB == "Unknowns")

questioned_3 <- questioned_3 %>%
  ungroup(BarrelA) %>%
  mutate(
    BarrelA = factor(factor(BarrelA), levels = c("KF", "KG", "KH", "KI", "KJ", "Unknowns")),
    BulletB = factor(BulletB, levels = rev(c("U14", "U27", "U33", "U36", "U45", "U49", "U56", "U65"))),
    BulletA = factor(BulletA, levels = c("1", "2", "3", rev(levels(BulletB))))
  )

```

```{r}
f2_1 <- f2_1 %>% mutate(
  samesource = ifelse(questioned_1$samesource == "TRUE" & f2_1$samesource == "FALSE", TRUE, samesource)
)

f2_2 <- f2_2 %>% mutate(
  samesource = ifelse(questioned_2$samesource == "TRUE" & f2_2$samesource == "FALSE", TRUE, samesource)
)


f2_3 <- f2_3 %>% mutate(
  samesource = ifelse(questioned_3$samesource == "TRUE" & f2_3$samesource == "FALSE", TRUE, samesource)
)

```


```{r}
library(caret)
set.seed(91191199)#20140501
inTraining_p <- createDataPartition(f2_1$samesource, p = .80, list = FALSE)
training_p <- f2_1[ inTraining_p,]
testing_p  <- f2_1[-inTraining_p,]
```

```{r} 
#Model1
fitControl <- trainControl(## 10-fold CV
                           method ='repeatedcv',
                           number = 10,
                           repeats = 3,
                           search = 'random')

mtry <- sqrt(ncol(training_p))
tunegrid <- expand.grid(.mtry=mtry)
model1 <- train(as.factor(samesource) ~ ccf
                 +rough_cor
                 +D
                 +sd_D
                 +matches
                 +mismatches
                 +cms+non_cms
                 +sum_peaks, 
                 data = training_p, 
                 method = "rf",
                 tuneLength = 15,
                 trControl = fitControl)

print(model1)

rf_pred1 <- predict(model1, testing_p)
confusionMatrix(rf_pred1, as.factor(testing_p$samesource))
```

