---
title: "Houston Rerun"
author: "Andrew Maloney"
date: "9/4/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
# Loading Packages
library(dplyr)
library(bulletxtrctr)
library(x3ptools)
library(ggplot2)
library(readr)
library(purrr)
library(stringr)
library(tidyr)


```

***Notes***
Bullets from the same barrel are considered matches.
Bullets from different barrels are not considered matches.
In case a bullet is unknown, we do not know whether there is a match or not.

Lands from the same bullet are considered matches if they are from the same barrel.
In case the lands are from bullets from different barrels they are not matches.

***Questions to be Answered***
There are a few key relationships we are trying to determine when comparing two Barrel-Bullet-Land IDs:
- Matches between questioned and known bullets
- Matches between questioned and other questioned bullets
- Same lands between different bullets from the same barrel.
- Same lands between any questioned bullets with any other bullet.

```{r}
# Determining Ground Truth 

features_1 <- comparisons_1 %>% select(-cms2_per_mm, -cms_per_mm, -lag_mm, -length_mm, -matches_per_mm, -mismatches_per_mm, -non_cms_per_mm, -rfscore)

features_1 <- features_1 %>% mutate(
  samesource = ifelse(BarrelA==BarrelB & BulletA == BulletB, LandA==LandB, NA),
  samebarrel = BarrelA == BarrelB,
  samebarrel = ifelse((BarrelA == "Unknowns" | BarrelB == "Unknowns") & (BulletA != BulletB), NA, samebarrel),
  samesource = ifelse(!samebarrel, FALSE, samesource)
  )


features_1 <- features_1 %>% mutate(comparison = paste0(pmin(Bullet1, Bullet2)," vs ", pmax(Bullet1, Bullet2)))

head(features_1)

#-----------------------------------------------------------------------------------------------

features_2 <- comparisons_2 %>% select(-cms2_per_mm, -cms_per_mm, -lag_mm, -length_mm, -matches_per_mm, -mismatches_per_mm, -non_cms_per_mm, -rfscore)

features_2 <- features_2 %>% mutate(
  samesource = ifelse(BarrelA==BarrelB & BulletA == BulletB, LandA==LandB, NA),
  samebarrel = BarrelA == BarrelB,
  samebarrel = ifelse((BarrelA == "Unknowns" | BarrelB == "Unknowns") & (BulletA != BulletB), NA, samebarrel),
  samesource = ifelse(!samebarrel, FALSE, samesource)
  )


features_2 <- features_2 %>% mutate(comparison = paste0(pmin(Bullet1, Bullet2)," vs ", pmax(Bullet1, Bullet2)))

head(features_2)

#-------------------------------------------------------------------------------------------------


features_3 <- comparisons_3 %>% select(-cms2_per_mm, -cms_per_mm, -lag_mm, -length_mm, -matches_per_mm, -mismatches_per_mm, -non_cms_per_mm, -rfscore)

features_3 <- features_3 %>% mutate(
  samesource = ifelse(BarrelA==BarrelB & BulletA == BulletB, LandA==LandB, NA),
  samebarrel = BarrelA == BarrelB,
  samebarrel = ifelse((BarrelA == "Unknowns" | BarrelB == "Unknowns") & (BulletA != BulletB), NA, samebarrel),
  samesource = ifelse(!samebarrel, FALSE, samesource)
  )


features_3 <- features_3 %>% mutate(comparison = paste0(pmin(Bullet1, Bullet2)," vs ", pmax(Bullet1, Bullet2)))

head(features_3)
```


***Explanation***
We have created three new features:
samesource - 1/6 between Barrel-Bullet-Land Scores
samebarrel - Same Barrels when being compared or not the same Barrels when being compared
comparison - Essential an ID column saying which Barrel-Bullet-Lands are being compared

```{r}

features_1 <- features_1 %>% select(-cms2, -lag, -length) # Cleaning for future exploration
features_2 <- features_2 %>% select(-cms2, -lag, -length)
features_3 <- features_3 %>% select(-cms2, -lag, -length)

```

***Notes Part 2***
We are going to calculate:
- "bestlandmatch" using SAM scores to determine which lands match the best between any two bullets

- "sameland_pred" is to check if the SAM score is significantly higher than the non-matching lands(based on a bootsrap)

- "samebarrel_pred" is the maximum for each bullet to bulelt comparison

```{r}

f2nest_1 <- features_1 %>% 
  group_by(BarrelA, BulletA, BarrelB, BulletB) %>%  nest()  


f3nest_1 <- f2nest_1 %>% mutate(
  sam_ccf = data %>% purrr::map_dbl(.f=function(d) 
    max(bulletxtrctr::compute_average_scores(d$LandA, d$LandB, d$ccf, addNA = TRUE)))
  )



f3nest_1 <- f3nest_1 %>% mutate(
  data = data %>% purrr::map(.f=function(d) {
    d$bestlandmatch = bulletxtrctr::bullet_to_land_predict(d$LandA, d$LandB, d$ccf, difference=-1, alpha = 1, addNA = FALSE)    
    d
  })
  )


f3nest_1 <- f3nest_1 %>% mutate(
  data = data %>% purrr::map(.f=function(d) {
    d$sameland_pred = bulletxtrctr::bullet_to_land_predict(d$LandA, d$LandB, d$ccf, difference=0.1, alpha = 0.05, addNA = FALSE)    
    d
  })
  )

f3nest_1 <- f3nest_1 %>% mutate(
  samebarrel_pred = data %>% purrr::map_dbl(.f=function(d) 
    max(d$sameland_pred))
  )

#--------------------------------------------------------------------------------

f2nest_2 <- features_2 %>% 
  group_by(BarrelA, BulletA, BarrelB, BulletB) %>%  nest()  


f3nest_2 <- f2nest_2 %>% mutate(
  sam_ccf = data %>% purrr::map_dbl(.f=function(d) 
    max(bulletxtrctr::compute_average_scores(d$LandA, d$LandB, d$ccf, addNA = TRUE)))
  )



f3nest_2 <- f3nest_2 %>% mutate(
  data = data %>% purrr::map(.f=function(d) {
    d$bestlandmatch = bulletxtrctr::bullet_to_land_predict(d$LandA, d$LandB, d$ccf, difference=-1, alpha = 1, addNA = FALSE)    
    d
  })
  )


f3nest_2 <- f3nest_2 %>% mutate(
  data = data %>% purrr::map(.f=function(d) {
    d$sameland_pred = bulletxtrctr::bullet_to_land_predict(d$LandA, d$LandB, d$ccf, difference=0.1, alpha = 0.05, addNA = FALSE)    
    d
  })
  )

f3nest_2 <- f3nest_2 %>% mutate(
  samebarrel_pred = data %>% purrr::map_dbl(.f=function(d) 
    max(d$sameland_pred))
  )

#--------------------------------------------------------------------------------

f2nest_3 <- features_3 %>% 
  group_by(BarrelA, BulletA, BarrelB, BulletB) %>%  nest()  


f3nest_3 <- f2nest_3 %>% mutate(
  sam_ccf = data %>% purrr::map_dbl(.f=function(d) 
    max(bulletxtrctr::compute_average_scores(d$LandA, d$LandB, d$ccf, addNA = TRUE)))
  )



f3nest_3 <- f3nest_3 %>% mutate(
  data = data %>% purrr::map(.f=function(d) {
    d$bestlandmatch = bulletxtrctr::bullet_to_land_predict(d$LandA, d$LandB, d$ccf, difference=-1, alpha = 1, addNA = FALSE)    
    d
  })
  )


f3nest_3 <- f3nest_3 %>% mutate(
  data = data %>% purrr::map(.f=function(d) {
    d$sameland_pred = bulletxtrctr::bullet_to_land_predict(d$LandA, d$LandB, d$ccf, difference=0.1, alpha = 0.05, addNA = FALSE)    
    d
  })
  )

f3nest_3 <- f3nest_3 %>% mutate(
  samebarrel_pred = data %>% purrr::map_dbl(.f=function(d) 
    max(d$sameland_pred))
  )


```

***Notes on Newly created features***
bestlandmatch and sameland_pred are both nested currently in the data column.  This column is a tibble. 
samebarrel_pred is showing the lands for each barrel comparisons of which have the higher sameland_pred scores.  It seems to be the first 3 lands between BulletA and BulletB.

##Check Predictions
- Now use "bestlandmatch to identify matching lands betweem different bullets from the same barrel

```{r}

f3long_1 <- f3nest_1 %>% 
  filter(BarrelA==BarrelB, BulletA != BulletB, BarrelA != "Unknowns") %>%
    unnest(data) 

f3long_1 %>%
  ggplot(aes(x = LandA, y = LandB, fill=ccf)) +
  geom_tile() +
  facet_wrap(~BarrelA+BulletA+BulletB) +
  scale_fill_gradient2(low="darkgrey", high="darkorange", midpoint=.5) +
  scale_colour_manual(values="darkorange") +
  geom_point(colour="red", data = f3long_1 %>% filter(bestlandmatch))+
  ggtitle("Houston_Group_1")


#---------------------------------------------------------------------

f3long_2 <- f3nest_2 %>% 
  filter(BarrelA==BarrelB, BulletA != BulletB, BarrelA != "Unknowns") %>%
    unnest(data)

f3long_2 %>%
  ggplot(aes(x = LandA, y = LandB, fill=ccf)) +
  geom_tile() +
  facet_wrap(~BarrelA+BulletA+BulletB) +
  scale_fill_gradient2(low="darkgrey", high="darkorange", midpoint=.5) +
  scale_colour_manual(values="darkorange") +
  geom_point(colour="red", data = f3long_2 %>% filter(bestlandmatch))+
  ggtitle("Houston_Group_2")

#--------------------------------------------------------------------

f3long_3 <- f3nest_3 %>% 
  filter(BarrelA==BarrelB, BulletA != BulletB, BarrelA != "Unknowns") %>%
    unnest(data)

f3long_3 %>%
  ggplot(aes(x = LandA, y = LandB, fill=ccf)) +
  geom_tile() +
  facet_wrap(~BarrelA+BulletA+BulletB) +
  scale_fill_gradient2(low="darkgrey", high="darkorange", midpoint=.5) +
  scale_colour_manual(values="darkorange") +
  geom_point(colour="red", data = f3long_3 %>% filter(bestlandmatch))+
  ggtitle("Houston_Group_3")

```

```{r}

#Distribution of best land matches from f3long_1,_2,_3

table(f3long_1$bestlandmatch)
table(f3long_2$bestlandmatch)
table(f3long_3$bestlandmatch)

```

```{r}

#Distribution of samesource for features_1,_2,_3

table(features_1$samesource)
table(features_2$samesource)
table(features_3$samesource)

```

```{r}

#Distribution of samebarrel for features_1,_2,_3
table(features_1$samebarrel)
table(features_2$samebarrel)
table(features_3$samebarrel)
```

```{r}

features_1 <- f3nest_1 %>% unnest(data)

features_1 <- features_1 %>% mutate(
  samesource = ifelse(BarrelA==BarrelB & BulletA!=BulletB & BarrelA != "Unknowns", bestlandmatch, samesource)
)


table(features_1$samesource)

f3nest_1 <- features_1 %>% 
  group_by(comparison,BarrelA, BulletA, BarrelB, BulletB, samebarrel, samebarrel_pred,
           sam_ccf, Bullet1, Bullet2) %>%  nest() 

#---------------------------------------------------------------------------------------------

features_2 <- f3nest_2 %>% unnest(data)

features_2 <- features_2 %>% mutate(
  samesource = ifelse(BarrelA==BarrelB & BulletA!=BulletB & BarrelA != "Unknowns", bestlandmatch, samesource)
)


table(features_2$samesource)

f3nest_2 <- features_2 %>% 
  group_by(comparison,BarrelA, BulletA, BarrelB, BulletB, samebarrel, samebarrel_pred,
           sam_ccf, Bullet1, Bullet2) %>%  nest() 

#--------------------------------------------------------------------------------------------------

features_3 <- f3nest_3 %>% unnest(data)

features_3 <- features_3 %>% mutate(
  samesource = ifelse(BarrelA==BarrelB & BulletA!=BulletB & BarrelA != "Unknowns", bestlandmatch, samesource)
)


table(features_3$samesource)

f3nest_3 <- features_3 %>% 
  group_by(comparison,BarrelA, BulletA, BarrelB, BulletB, samebarrel, samebarrel_pred,
           sam_ccf, Bullet1, Bullet2) %>%  nest() 

```

```{r}

f3nest_1 <- f3nest_1 %>% mutate(
  truth = c("different-source", "same-source")[samebarrel+1],
  truth = ifelse(is.na(samebarrel), "Unknown", truth),
  prediction = c("different-source", "same-source")[samebarrel_pred+1]
) 


f3nest_1 %>% group_by(comparison) %>%
  summarise(sam_ccf = mean(sam_ccf),
            truth = truth[1],
            prediction = prediction[1]) %>% 
  ggplot(aes(x = sam_ccf, y = truth, colour = prediction)) + geom_jitter() +
  theme_bw() +
  scale_colour_manual(values=c("darkgrey", "darkorange"))+
  ggtitle("Houston_Group_1")

#----------------------------------------------------------

f3nest_2 <- f3nest_2 %>% mutate(
  truth = c("different-source", "same-source")[samebarrel+1],
  truth = ifelse(is.na(samebarrel), "Unknown", truth),
  prediction = c("different-source", "same-source")[samebarrel_pred+1]
) 


f3nest_2 %>% group_by(comparison) %>%
  summarise(sam_ccf = mean(sam_ccf),
            truth = truth[1],
            prediction = prediction[1]) %>% 
  ggplot(aes(x = sam_ccf, y = truth, colour = prediction)) + geom_jitter() +
  theme_bw() +
  scale_colour_manual(values=c("darkgrey", "darkorange"))+
  ggtitle("Houston_Group_2")

#-----------------------------------------------------------------------------

f3nest_3 <- f3nest_3 %>% mutate(
  truth = c("different-source", "same-source")[samebarrel+1],
  truth = ifelse(is.na(samebarrel), "Unknown", truth),
  prediction = c("different-source", "same-source")[samebarrel_pred+1]
) 


f3nest_3 %>% group_by(comparison) %>%
  summarise(sam_ccf = mean(sam_ccf),
            truth = truth[1],
            prediction = prediction[1]) %>% 
  ggplot(aes(x = sam_ccf, y = truth, colour = prediction)) + geom_jitter() +
  theme_bw() +
  scale_colour_manual(values=c("darkgrey", "darkorange"))+
  ggtitle("Houston_Group_3")

```


```{r}

f3nest_1 %>% filter(truth =="different-source" & prediction=="same-source")

f3nest_2 %>% filter(truth =="different-source" & prediction=="same-source")

f3nest_3 %>% filter(truth =="different-source" & prediction=="same-source")

```

```{r}

table(f3nest_1$BulletA)

questioned_1 <- f3nest_1 %>% filter(BarrelB == "Unknowns")

questioned_1 <- questioned_1 %>%
  ungroup(BarrelA) %>%
  mutate(
    BarrelA = factor(factor(BarrelA), levels = c("KA", "KB", "KC", "KD", "KE", "Unknowns")),
    BulletB = factor(BulletB, levels = rev(c("U10", "U15", "U28", "U36", "U37", "U40", "U42", "U77"))),
    BulletA = factor(BulletA, levels = c("1", "2", "3", rev(levels(BulletB))))
  )

questioned_1 %>%
  ggplot(aes(x = BulletA, y = BulletB, fill=sam_ccf)) + 
  geom_tile(data = questioned_1) +
  scale_fill_gradient2(low="darkgrey", high="darkorange1", midpoint=.5) +
  scale_colour_manual(values=c("darkorange")) +
  facet_grid(.~BarrelA, space = "free", scales="free") +
  theme_bw() +
  geom_tile(colour = "black", size=1)+
  geom_point(colour = "red", data = questioned_1 %>% filter(samebarrel_pred==1))+
  ggtitle("Houston_Group_1")

```

```{r}

table(f3nest_2$BulletA)

questioned_2 <- f3nest_2 %>% filter(BarrelB == "Unknowns")

questioned_2 <- questioned_2 %>%
  ungroup(BarrelA) %>%
  mutate(
    BarrelA = factor(factor(BarrelA), levels = c("KC", "KD", "KE", "KF", "KG", "Unknowns")),
    BulletB = factor(BulletB, levels = rev(c("U23", "U34", "U41", "U61", "U63", "U66", "U73", "U98"))),
    BulletA = factor(BulletA, levels = c("1", "2", "3", rev(levels(BulletB))))
  ) 

questioned_2 %>%
  ggplot(aes(x = BulletA, y = BulletB, fill=sam_ccf)) + 
  geom_tile(data = questioned_2) +
  scale_fill_gradient2(low="darkgrey", high="darkorange1", midpoint=.5) +
  scale_colour_manual(values=c("darkorange")) +
  facet_grid(.~BarrelA, space = "free", scales="free") +
  theme_bw() +
  geom_tile(colour = "black", size=1)+
  geom_point(colour = "red", data = questioned_2 %>% filter(samebarrel_pred==1))+
  ggtitle("Houston_Group_2")

```

```{r}

table(f3nest_3$BarrelA)

questioned_3 <- f3nest_3 %>% filter(BarrelB == "Unknowns")

questioned_3 <- questioned_3 %>%
  ungroup(BarrelA) %>%
  mutate(
    BarrelA = factor(factor(BarrelA), levels = c("KF", "KG", "KH", "KI", "KJ", "Unknowns")),
    BulletB = factor(BulletB, levels = rev(c("U14", "U27", "U33", "U36", "U45", "U49", "U56", "U65"))),
    BulletA = factor(BulletA, levels = c("1", "2", "3", rev(levels(BulletB))))
  ) 

questioned_3 %>%
  ggplot(aes(x = BulletA, y = BulletB, fill=sam_ccf)) + 
  geom_tile(data = questioned_3) +
  scale_fill_gradient2(low="darkgrey", high="darkorange1", midpoint=.5) +
  scale_colour_manual(values=c("darkorange")) +
  facet_grid(.~BarrelA, space = "free", scales="free") +
  theme_bw() +
  geom_tile(colour = "black", size=1)+
  geom_point(colour = "red", data = questioned_3 %>% filter(samebarrel_pred==1))+
  ggtitle("Houston_Group_3")

```

```{r}

f3nest_1 <- f3nest_1 %>% ungroup(samebarrel) %>%
  mutate(
  samebarrel = ifelse(BarrelA == "Unknowns" & (BulletA != BulletB),
                      samebarrel_pred == 1, samebarrel)
)

#------------------------------------------------------------------------------------------

f3nest_2 <- f3nest_2 %>% ungroup(samebarrel) %>%
  mutate(
  samebarrel = ifelse(BarrelA == "Unknowns" & (BulletA != BulletB),
                      samebarrel_pred == 1, samebarrel)
)

#------------------------------------------------------------------------------------------

f3nest_3 <- f3nest_1 %>% ungroup(samebarrel) %>%
  mutate(
  samebarrel = ifelse(BarrelA == "Unknowns" & (BulletA != BulletB),
                      samebarrel_pred == 1, samebarrel)
)

```


```{r}

f3nest_1 <- f3nest_1 %>% mutate(
  samebarrel = ifelse(BarrelB == "Unknowns" & (BulletA != BulletB),
                      samebarrel_pred == 1, samebarrel)
)

#-----------------------------------------------------------------------------------------

f3nest_2 <- f3nest_2 %>% mutate(
  samebarrel = ifelse(BarrelB == "Unknowns" & (BulletA != BulletB),
                      samebarrel_pred == 1, samebarrel)
)

#------------------------------------------------------------------------------------------

f3nest_3 <- f3nest_3 %>% mutate(
  samebarrel = ifelse(BarrelB == "Unknowns" & (BulletA != BulletB),
                      samebarrel_pred == 1, samebarrel)
)

```


```{r}


f2_1 <- f3nest_1 %>% unnest(data)
f2_1 <- f2_1 %>% mutate(
  samesource = ifelse(is.na(samesource) & !samebarrel, FALSE, samesource),
  samesource = ifelse(is.na(samesource) & samebarrel, bestlandmatch, samesource)
)

```

```{r}
f2_2 <- f3nest_2 %>% unnest(data)
f2_2 <- f2_2 %>% mutate(
  samesource = ifelse(is.na(samesource) & !samebarrel, FALSE, samesource),
  samesource = ifelse(is.na(samesource) & samebarrel, bestlandmatch, samesource)
)

```

```{r}
f2_3 <- f3nest_3 %>% unnest(data)
f2_3 <- f2_3 %>% mutate(
  samesource = ifelse(is.na(samesource) & !samebarrel, FALSE, samesource),
  samesource = ifelse(is.na(samesource) & samebarrel, bestlandmatch, samesource)
)

```


```{r}
questioned_1 <- f2_1 %>% filter(BarrelB == "Unknowns")

questioned_1 <- questioned_1 %>%
  ungroup(BarrelA) %>%
  mutate(
    BarrelA = factor(factor(BarrelA), levels = c("KA", "KB", "KC", "KD", "KE", "Unknowns")),
    BulletB = factor(BulletB, levels = rev(c("U10", "U15", "U28", "U36", "U37", "U40", "U42", "U77"))),
    BulletA = factor(BulletA, levels = c("1", "2", "3", rev(levels(BulletB))))
  ) 

```


```{r}

questioned_2 <- f2_2 %>% filter(BarrelB == "Unknowns")

questioned_2 <- questioned_2 %>%
  ungroup(BarrelA) %>%
  mutate(
    BarrelA = factor(factor(BarrelA), levels = c("KC", "KD", "KE", "KF", "KG", "Unknowns")),
    BulletB = factor(BulletB, levels = rev(c("U23", "U34", "U41", "U61", "U63", "U66", "U73", "U98"))),
    BulletA = factor(BulletA, levels = c("1", "2", "3", rev(levels(BulletB))))
  ) 

```


```{r}
questioned_3 <- f2_3 %>% filter(BarrelB == "Unknowns")

questioned_3 <- questioned_3 %>%
  ungroup(BarrelA) %>%
  mutate(
    BarrelA = factor(factor(BarrelA), levels = c("KF", "KG", "KH", "KI", "KJ", "Unknowns")),
    BulletB = factor(BulletB, levels = rev(c("U14", "U27", "U33", "U36", "U45", "U49", "U56", "U65"))),
    BulletA = factor(BulletA, levels = c("1", "2", "3", rev(levels(BulletB))))
  )

```


```{r}

table(f2_1$samesource)
table(f2_2$samesource)
table(f2_3$samesource)

```

```{r}
f2_1 <- f2_1 %>% mutate(
  samesource = ifelse(questioned_1$samesource == "TRUE" & f2_1$samesource == "FALSE", TRUE, samesource)
)

f2_2 <- f2_2 %>% mutate(
  samesource = ifelse(questioned_2$samesource == "TRUE" & f2_2$samesource == "FALSE", TRUE, samesource)
)


f2_3 <- f2_3 %>% mutate(
  samesource = ifelse(questioned_3$samesource == "TRUE" & f2_3$samesource == "FALSE", TRUE, samesource)
)

```

```{r}

table(f2_1$samesource)
table(f2_2$samesource)
table(f2_3$samesource)

```





