---
title: "Phoenix Rerun"
author: "Andrew Maloney"
date: "11/7/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
# Loading Packages
library(dplyr)
library(bulletxtrctr)
library(x3ptools)
library(ggplot2)
library(readr)
library(purrr)
library(stringr)
library(tidyr)
```

```{r eval=FALSE, include=FALSE}
Phoenix <- tibble(path = list.files(path = "/media/Sunny/CSAFE/Phoenix Set",
                                    pattern = ".x3p", recursive = T, full.names = T)) %>% 
          mutate(Barrel = str_extract(path, "(Unknown|Gun [0-9]-[A-Z][0-9])") %>%
                   str_remove("Gun 1-"),
                 Bullet = str_extract(path, "(B[0-9]|Unknown 1-[A-Z])") %>%
                   str_remove("Unknown 1-"),
                 Land = str_extract(path, "/L[0-9]") %>%
                   str_remove("/L")) %>%
          mutate(x3p = map(path, read_x3p))
```

```{r}
load("Ground_Truth_Data.RData") 
#For Html Purposes

```

```{r}
#Checking scan orientation

image(Phoenix$x3p[[1]])
image(Phoenix$x3p[[10]])
image(Phoenix$x3p[[100]])
image(Phoenix$x3p[[200]])

```

***Notes***
Bullets from the same barrel are considered matches.
Bullets from different barrels are not considered matches.
In case a bullet is unknown, we do not know whether there is a match or not.

Lands from the same bullet are considered matches if they are from the same barrel.
In case the lands are from bullets from different barrels they are not matches.

***Questions to be Answered***
There are a few key relationships we are trying to determine when comparing two Barrel-Bullet-Land IDs:
- Matches between questioned and known bullets
- Matches between questioned and other questioned bullets
- Same lands between different bullets from the same barrel.
- Same lands between any questioned bullets with any other bullet.


```{r}
# Determining Ground Truth
# These features were obtained from the 2019 summer Bullet Project
# Features were extracted from Bullet-Barrel-Land scans using the x3ptools & bulletxtrctr packages

features <- Phoenix_Comparisons %>% 
  select(-cms2_per_mm, -cms_per_mm, -lag_mm, -length_mm, 
         -matches_per_mm, -mismatches_per_mm, -non_cms_per_mm, -rfscore)

features <- features %>% mutate(
  samesource = ifelse(BarrelA==BarrelB & BulletA == BulletB, LandA==LandB, NA),
  samebarrel = BarrelA == BarrelB,
  samebarrel = ifelse((BarrelA == "Unknown" | BarrelB == "Unknown") & (BulletA != BulletB), NA, samebarrel), 
  samesource = ifelse(!samebarrel, FALSE, samesource)
  )

features <- features %>% mutate(
  comparison = paste0(pmin(Bullet1, Bullet2)," vs ", pmax(Bullet1, Bullet2))
)

```

***Explanation***
We have created three new features:
samesource - 1/6 between Barrel-Bullet-Land Scores
samebarrel - Same Barrels when being compared or not the same Barrels when being compared
comparison - Essential an ID column saying which Barrel-Bullet-Lands are being compared


```{r}

head(features, 10)

features <- features %>% select(-cms2, -lag, -length) # Cleaning for future exploration

head(features, 10)

```

***Notes Part 2***
We are going to calculate:
- "bestlandmatch" using SAM scores to determine which lands match the best between any two bullets

- "sameland_pred" is to check if the SAM score is significantly higher than the non-matching lands(based on a bootsrap)

- "samebarrel_pred" is the maximum for each bullet to bulelt comparison

```{r}

f2nest <- features %>%
  group_by(BarrelA, BulletA, BarrelB, BulletB) %>% nest()

f3nest <- f2nest %>% mutate(
  sam_ccf = data %>% purrr::map_dbl(.f=function(d) 
    max(bulletxtrctr::compute_average_scores(d$LandA, d$LandB, d$ccf, addNA = TRUE)))
  )

```

```{r}

head(f3nest)


```

```{r}

f3nest <- f3nest %>% mutate(
  data = data %>% purrr::map(.f = function(d) {
    d$bestlandmatch = bulletxtrctr::bullet_to_land_predict(d$LandA, d$LandB, d$ccf, difference = -1, alpha = 1, addNA = FALSE)
    d
  })
)

```

```{r}

head(f3nest)

```

```{r}

f3nest <- f3nest %>% mutate(
  data = data %>% purrr::map(.f = function(d) {
    d$sameland_pred = bulletxtrctr::bullet_to_land_predict(d$LandA, d$LandB, d$ccf, difference = 0.1, alpha = 0.05, addNA = FALSE)
    d
  })
)

```

```{r}

head(f3nest)

```

```{r}

f3nest <- f3nest %>% mutate(
  samebarrel_pred = data %>% purrr::map_dbl(.f = function(d)
    max(d$sameland_pred))
)

```

```{r}

head(f3nest)

```

***Notes on Newly created features***
bestlandmatch and sameland_pred are both nested currently in the data column.  This column is a tibble. 
samebarrel_pred is showing the lands for each barrel comparisons of which have the higher sameland_pred scores.  It seems to be the first 3 lands between BulletA and BulletB.

##Check Predictions
- Now use "bestlandmatch to identify matching lands betweem different bullets from the same barrel

```{r}

f3long <- f3nest %>% 
  filter(BarrelA == BarrelB, BulletA != BulletB, BarrelA != "Unknown") %>%
    unnest(data) # Only looking at Barrels that are the same

```

```{r}

head(f3long)

```

###Let's Plot some Heat Maps

```{r}

f3long %>%
  ggplot(aes(x = LandA, y = LandB, fill = ccf))+
  geom_tile()+
  facet_wrap(~BarrelA+BulletA)+
  scale_fill_gradient2(low = "darkgrey", high = "darkorange", midpoint = 0.5)+
  scale_colour_manual(values = "darkorange")+
  geom_point(colour = "midnightblue", data = f3long %>% filter(bestlandmatch))

```

```{r}

f3long %>%
  ggplot(aes(x = LandA, y = LandB, fill = ccf))+
  geom_tile()+
  facet_wrap(~BarrelA+BulletA+BulletB)+
  scale_fill_gradient2(low = "darkgrey", high = "darkorange", midpoint = 0.5)+
  scale_colour_manual(values = "darkorange")+
  geom_point(colour = "midnightblue", data = f3long %>% filter(bestlandmatch))

```

```{r}
#Distribution of best land matches from f3long
table(f3long$bestlandmatch)

```

```{r}
#Distribution of samesource
table(features$samesource)

```

```{r}
#Distribution of samebarrel
table(features$samebarrel)


```

There seems to be a small amount of missing data. Barrel C8, Bullet B1, Land 3 is missing.  Barrel U1, Bullet B3, Land 5 is missing.  

Investigate the missing data Barrels C8 and U1
--- id: C8-B1-3 and U1-B3-5 are missing in the original phoenix data_set

#Eye-Catchers(Best Land Matches that are not high ccf values):

Barrel F6: B1|B3(4,3), B2|B3(2,3) 
Barrel L5: B1|B2(1,2), B2|B3(2,1)
Barrel M2: B1|B2(1,2), B2|B3(2,5)
Barrel R3: B1|B3(4,5)+(5,6) [Weird but also same exact ccf values but differnt bullet comparisons] B2|B3(4,5)+(5,6)
Barrel U1: B1|B2(1,3)+(2,4), B1|B3(2,6) 

F6-B1-4 vs F6-B3-3: samebarrel = TRUE, bestlandmatch = TRUE, sameland_pred = TRUE, ccf = 0.52, sam_ccf = 0.72, (matches and mismatches both = 18?, overlap = 1.00)

F6-B2-2 vs F6-B3-3: samebarrel = TRUE, beslandmatch = TRUE, sameland_pred = TRUE, ccf = 0.49, sam_ccf = 0.71, (matches = 28, mismatches = 11, overlap = 0.99)

```{r}
# F6-B1-4 and F6-B3-3
# F6-B2-2 and F6-B3-3

image(Phoenix$x3p[[39]])
image(Phoenix$x3p[[50]])

image(Phoenix$x3p[[43]])
image(Phoenix$x3p[[50]])

# F6-B1-4 and F6-B2-2 seem to be in very bad shape
```

```{r}

#### Barrel M2: B1|B2(1,2), B2|B3(2,5)

# M2-B1-1 and M2-B2-2
# M2-B2-2 and M2-B2-5

image(Phoenix$x3p[[72]])
image(Phoenix$x3p[[79]])

image(Phoenix$x3p[[79]])
image(Phoenix$x3p[[82]])

#Lands 1, 2, and 5 seem to have similar damage near the heal of the bullet

```

```{r}



#### Barrel R3: B1|B3(4,5)+(5,6) [Weird but also same exact ccf values but differnt bullet comparisons] B2|B3(4,5)+(5,6)

# R3-B1-4 and R3-B3-5
# R3-B1-5 and R3-B3-6
# R3-B2-4 and R3-B3-5
# R3-B2-5 and R3-B3-6

image(Phoenix$x3p[[111]])
image(Phoenix$x3p[[124]])

image(Phoenix$x3p[[112]])
image(Phoenix$x3p[[125]])

image(Phoenix$x3p[[117]])
image(Phoenix$x3p[[124]])

image(Phoenix$x3p[[118]])
image(Phoenix$x3p[[125]])

```

```{r}

features <- f3nest %>% unnest(data)

features <- features %>% mutate(
  samesource = ifelse(BarrelA == BarrelB & BulletA != BulletB & BarrelA != "Unknown", bestlandmatch, samesource)
)

```

```{r}

head(features, 10)

```

```{r}
#Description of features same source, FALSE and TRUE both increased in entries
table(features$samesource)

```

```{r}

f3nest <- features %>%
  group_by(comparison, BarrelA, BulletA, BarrelB, 
           BulletB, samebarrel, samebarrel_pred, sam_ccf,
           Bullet1, Bullet2) %>% nest()

```

***Matches with questioned bullets***

Any matches with questioned bullets are based on predictions only.
Ground truth can only be determined in collaboration with the owners of the study. 

This affects all of the following open questions:
-matches between questioned and known bullets
- matches between questioned and other questioned bullets
- same lands between any questioned bullets woth any other bullets

In comparing known samesource(base on bootstrap) we expect to see orange dots(predicted samesource) for known samesource and gray dots(predicted different source) for known different source comparisons $(*)

```{r}

f3nest <- f3nest %>% mutate(
  truth = c("different-source", "same-source")[samebarrel+1],
  truth = ifelse(is.na(samebarrel), "Unknown", truth),
  prediction = c("different-source", "same-source")[samebarrel_pred+1]
)

```

```{r}
# plot $(*)

f3nest %>% group_by(comparison) %>%
  summarise(sam_ccf = mean(sam_ccf),
            truth = truth[1],
            prediction = prediction[1]) %>%
  ggplot(aes(x = sam_ccf, y = truth, colour = prediction))+
  geom_jitter()+
  theme_bw()+
  scale_colour_manual(values = c("darkgrey", "darkorange"))

```

***Graph Analysis***
Looking at the graph above we can see many points plotted but what is being described here?  We have 3 sources which are "same-source", "different-source", and "Unknown."

Our results look very good.  We would expect to see same-source points plotted around higher sam_ccf scores and different-source points plotted at the lower end of sam_ccf scores.  The Predicted "same-source" points are ploted around the true "same-source" points. The predicted "different-source" points are plotted arund the true "different-source" points.  For the true "unknown" barrels in question, we see a mix of predicted "different source" and "same-source" points.  There doesn't seem to be any predicted "different-source"" points plotted around the true "same-source" area and vice versus.  These results are exactly what we were hoping for.

```{r}
#There does not seem to be any recognized truth that is dofferent than the predictions

f3nest %>% filter(truth == "different-source" & prediction == "same-source")

```



```{r}
#Filter for questioned bullets
questioned <- f3nest %>% filter(BarrelB == "Unknown")

```

```{r}

table(questioned$BarrelA)

```

```{r}

questioned <- questioned %>%
  ungroup(BarrelA) %>%
  mutate(
    BarrelA = factor(factor(BarrelA), levels = c("A9", "C8", "F6", "L5", "M2", "P7", "R3", "U1", "Unknown")),
    BulletB = factor(BulletB, levels = rev(c("B", "E", "H", "J", "K", "N", "Q", "T", "Y", "Z"))),
    BulletA = factor(BulletA, levels = c("B1", "B2", "B3", rev(levels(BulletB))))
  ) 



questioned %>%
  ggplot(aes(x = BulletA, y = BulletB, fill=sam_ccf)) + 
  geom_tile(data = questioned) +
  scale_fill_gradient2(low="darkgrey", high="darkorange", midpoint=.5) +
  scale_colour_manual(values=c("darkorange")) +
  facet_grid(.~BarrelA, space = "free", scales="free") +
  theme_bw() +
  geom_point(colour = "midnightblue", data = questioned %>% filter(samebarrel_pred==1))

```

The figure suggests that mostly, we should be able to accept the same-source predictions for each of the barrels as ground truth.
In particular, concistency in the matches between a questioned bullet and a single barrel provide strong evidence in the correctness of a prediction: 
ideally, we would like to see a match between 
- a questioned bullet and all three bullets of a single barrel
- questioned bullets that match to the same barrel

This is true for all unknown bullets with the exception of bullets Q, Y, and Z. 
Bullets Q, Y, and Z match to none of the bullets of any barrel. 

```{r}

f3nest <- f3nest %>% ungroup(samebarrel) %>%
  mutate(
  samebarrel = ifelse(BarrelA == "Unknown" & (BulletA != BulletB),
                      samebarrel_pred == 1, samebarrel)
)

```

```{r}

f3nest <- f3nest %>% mutate(
  samebarrel = ifelse(BarrelB == "Unknown" & (BulletA != BulletB),
                      samebarrel_pred == 1, samebarrel)
)

```


```{r}

head(f3nest)


```

```{r}

f2 <- f3nest %>% unnest(data)
f2 <- f2 %>% mutate(
  samesource = ifelse(is.na(samesource) & !samebarrel, FALSE, samesource),
  samesource = ifelse(is.na(samesource) & samebarrel, bestlandmatch, samesource)
)

```

```{r}

head(f2)

```

```{r}
questioned <- f2 %>% filter(BarrelB == "Unknown")

questioned <- questioned %>%
  ungroup(BarrelA) %>%
  mutate(
    BarrelA = factor(factor(BarrelA), levels = c("A9", "C8", "F6", "L5", "M2", "P7", "R3", "U1", "Unknown")),
    BulletB = factor(BulletB, levels = rev(c("B", "E", "H", "J", "K", "N", "Q", "T", "Y", "Z"))),
    BulletA = factor(BulletA, levels = c("B1", "B2", "B3", rev(levels(BulletB))))
  ) 


questioned %>%
  ggplot(aes(x = LandA, y = LandB, fill=ccf)) + geom_tile() +
  scale_fill_gradient2(low="darkgrey", high="darkorange", midpoint=.5) +
  facet_grid(BulletB~BarrelA+BulletA) +
  geom_point(colour = "red", data = questioned %>% filter(samesource))

```



```{r}
table(f2$samesource)
```

```{r}
f2 <- f2 %>% mutate(
  samesource = ifelse(questioned$samesource == "TRUE" & f2$samesource == "FALSE", TRUE, samesource)
)

```

```{r}
table(f2$samesource)
```



Accuracy for models is around the same.  Now we will try and find miss classified ground truth results by examining signatures between Barrel_Bullet_Land comparisons.
```{r}

Signatures_Phoenix %>%
  filter(Barrel != "Unknown") %>%
    ggplot(data = ., aes(x = x, y = sig, color = Land)) + 
      geom_line()+
        facet_grid(paste("Bullet", Bullet) ~ sprintf("Barrel %02s", Barrel))+
          theme_bw()+
            ggtitle("Signatures for Known Barrels")

Signatures_Phoenix %>%
  filter(Barrel == "Unknown") %>%
    ggplot(data = ., aes(x = x, y = sig, color = Land)) + 
      geom_line()+
        facet_wrap(paste("Bullet", Bullet) ~ sprintf("Barrel %02s", Barrel))+
          theme_bw()+
            ggtitle("Signatures for Questioned Bullets")

```

```{r}
# High ccf & samesource('FALSE')


f2 %>% 
  filter(ccf >= 0.70 & samesource == "FALSE")


Signatures_Phoenix %>% 
  filter(id %in% c("L5-B1-3", "P7-B3-5")) %>% #Not a Match
ggplot(data = ., aes(x = x, y = sig, color = Bullet)) + 
  geom_line()+
    theme_bw()+
  scale_color_brewer(palette = "Dark2")+
    ggtitle("L5-B1-3 VS P7-B3-5")

Signatures_Phoenix %>% 
  filter(id %in% c("L5-B1-3", "Unknown-J-5")) %>% #Possibly a Match(sum peaks suggest strong match)
ggplot(data = ., aes(x = x, y = sig, color = Bullet)) + 
  geom_line()+
    theme_bw()+
  scale_color_brewer(palette = "Dark2")+
    ggtitle("L5-B1-3 VS Unknown-J-5")

Signatures_Phoenix %>% 
  filter(id %in% c("L5-B2-2", "U1-B1-1")) %>% #Possibly a Match(sum peaks suggest strong match)
ggplot(data = ., aes(x = x, y = sig, color = Bullet)) + 
  geom_line()+
    theme_bw()+
  scale_color_brewer(palette = "Dark2")+
    ggtitle("L5-B2-2 vs U1-B1-1")

Signatures_Phoenix %>% 
  filter(id %in% c("M2-B2-4", "Unknown-B-2")) %>% #Match(sum peaks suggest strong match)
ggplot(data = ., aes(x = x, y = sig, color = Bullet)) + 
  geom_line()+
    theme_bw()+
  scale_color_brewer(palette = "Dark2")+
    ggtitle("M2-B2-4 vs Unknown-B-2")

Signatures_Phoenix %>% 
  filter(id %in% c("P7-B3-5", "Unknown-T-3")) %>% #Not a Match
ggplot(data = ., aes(x = x, y = sig, color = Bullet)) + 
  geom_line()+
    theme_bw()+
  scale_color_brewer(palette = "Dark2")+
    ggtitle("P7-B3-5 vs Unknown-T-3")

Signatures_Phoenix %>% 
  filter(id %in% c("Unknown-J-5", "Unknown-T-3")) %>% #Not a Match
ggplot(data = ., aes(x = x, y = sig, color = Bullet)) + 
  geom_line()+
    theme_bw()+
  scale_color_brewer(palette = "Dark2")+
    ggtitle("Unknown-J-5 vs Unknown-T-3")

# Analyze signatures for these comparisons

```


```{r}

f2 <- f2 %>% mutate(
  samesource = ifelse(f2$comparison == "M2-B2-4 vs Unknown-B-2" & f2$samesource == "FALSE", TRUE, samesource)
)

```



