---
title: "Untitled"
author: "Andrew Maloney"
date: "12/29/2019"
output: html_document
---

Phoenix Machine Learning Models

```{r}

load("Ground_Truth_Data.RData") 

```

```{r}

# Loading Packages
library(dplyr)
library(bulletxtrctr)
library(x3ptools)
library(ggplot2)
library(readr)
library(purrr)
library(stringr)
library(tidyr)
library(caret)

```

```{r}

set.seed(20140501)#20140501
inTraining_p <- createDataPartition(f2$samesource, p = .80, list = FALSE)
training_p <- f2[ inTraining_p,]
testing_p  <- f2[-inTraining_p,]

#Model_1
fitControl <- trainControl(## 10-fold CV
                           method ='repeatedcv',
                           number = 10,
                           repeats = 3,
                           search = 'random')

mtry <- sqrt(ncol(training_p))
tunegrid <- expand.grid(.mtry=mtry)
model_1 <- train(as.factor(samesource) ~ ccf
                 +rough_cor
                 +D
                 +sd_D
                 +matches
                 +mismatches
                 +cms+non_cms
                 +sum_peaks, 
                 data = training_p, 
                 method = "rf",
                 tuneLength = 15,
                 trControl = fitControl)

print(model_1)

rf_pred_1 <- predict(model_1, testing_p)
confusionMatrix(rf_pred_1, as.factor(testing_p$samesource))

```

```{r}

set.seed(20140501)#20140501
inTraining_p <- createDataPartition(f2$samesource, p = .80, list = FALSE)
training_p <- f2[ inTraining_p,]
testing_p  <- f2[-inTraining_p,]

#Model_2
fitControl <- trainControl(## 10-fold CV
                           method ='repeatedcv',
                           number = 10,
                           repeats = 3,
                           search = 'random')

mtry <- sqrt(ncol(training_p))
tunegrid <- expand.grid(.mtry=mtry)
model_2 <- train(as.factor(samesource) ~ ccf
                 +rough_cor
                 +D
                 +sd_D
                 +matches
                 +mismatches
                 +cms+non_cms
                 +sum_peaks
                 +overlap,
                 data = training_p, 
                 method = "rf",
                 tuneLength = 15,
                 trControl = fitControl)

print(model_2)

rf_pred_2 <- predict(model_2, testing_p)
confusionMatrix(rf_pred_2, as.factor(testing_p$samesource))

```

```{r}
#Model_3

set.seed(91191199)#20140501
inTraining_p <- createDataPartition(f2$samesource, p = .80, list = FALSE)
training_p <- f2[ inTraining_p,]
testing_p  <- f2[-inTraining_p,]

fitControl <- trainControl(## 10-fold CV
                           method ='repeatedcv',
                           number = 10,
                           repeats = 3,
                           search = 'random')

mtry <- sqrt(ncol(training_p))
tunegrid <- expand.grid(.mtry=mtry)
model_3 <- train(as.factor(samesource) ~ ccf
                 +rough_cor
                 +D
                 +sd_D
                 +matches
                 +mismatches
                 +cms+non_cms
                 +sum_peaks
                 +overlap,
                 data = training_p, 
                 method = "rf",
                 tuneLength = 15,
                 trControl = fitControl)

print(model_3)

rf_pred_3 <- predict(model_3, testing_p)
confusionMatrix(rf_pred_3, as.factor(testing_p$samesource))

```

```{r}
#Model_4(grid_search tuning)
set.seed(20140501)#20140501
inTraining_p <- createDataPartition(f2$samesource, p = .80, list = FALSE)
training_p <- f2[ inTraining_p,]
testing_p  <- f2[-inTraining_p,]


fitControl <- trainControl(method="repeatedcv",
                            number=10, 
                              repeats=3,
                                search="grid")

tunegrid <- expand.grid(.mtry=c(1:15))

rf_gridsearch <- train(as.factor(samesource) ~ ccf
                 +rough_cor
                 +D
                 +sd_D
                 +matches
                 +mismatches
                 +cms+non_cms
                 +sum_peaks
                 +overlap,
                 data = training_p, 
                 method = "rf",
                 metric= "accuracy", 
                 tuneGrid=tunegrid, 
                 trControl=fitControl)

print(rf_gridsearch)
plot(rf_gridsearch)

```

We have tried some generic random forest algorithms using caret.
We can see that the model is performing with about 97% accuracy.

Looking at a confusion matrix, we can see alot of true's are being identified as false.
This is a result of our unblanced data.  We can conclude that there is bias within the prediction models towards the more common classification("false")

We are going to experiment with some over- and under-sampling with cross-validation resampling.
We are also going to try some hybrid algorithms such as ROSE and SMOTE



```{r}
#Model_5(Under-Sampling)

set.seed(20140501)#20140501
inTraining_p <- createDataPartition(f2$samesource, p = .80, list = FALSE)
training_p <- f2[ inTraining_p,]
testing_p  <- f2[-inTraining_p,]


fitControl <- trainControl(method="repeatedcv",
                            number=10, 
                              repeats=3,
                                sampling = "down")

rf_under <- train(as.factor(samesource) ~ ccf
                                        + rough_cor
                                        + D
                                        + sd_D
                                        + matches
                                        + mismatches
                                        + cms + non_cms
                                        + sum_peaks
                                        + overlap,
                  data = training_p,
                  method = "rf",
                  #preProcess = c("scale", "center"),
                  trControl = fitControl)
print(rf_under)

rf_pred_under <- predict(rf_under, testing_p)
confusionMatrix(rf_pred_under, as.factor(testing_p$samesource))

```

```{r}
#Model_6(Over-Sampling)

set.seed(20140501)#20140501
inTraining_p <- createDataPartition(f2$samesource, p = .80, list = FALSE)
training_p <- f2[ inTraining_p,]
testing_p  <- f2[-inTraining_p,]


fitControl <- trainControl(method="repeatedcv",
                            number=10, 
                              repeats=3,
                                sampling = "up")

rf_over <- train(as.factor(samesource) ~ ccf
                                        + rough_cor
                                        + D
                                        + sd_D
                                        + matches
                                        + mismatches
                                        + cms + non_cms
                                        + sum_peaks
                                        + overlap,
                  data = training_p,
                  method = "rf",
                  #preProcess = c("scale", "center"),
                  trControl = fitControl)
print(rf_over)

rf_pred_over <- predict(rf_over, testing_p)
confusionMatrix(rf_pred_over, as.factor(testing_p$samesource))


```

```{r}
#Model_7(ROSE) 



set.seed(20140501)#20140501
inTraining_p <- createDataPartition(f2$samesource, p = .80, list = FALSE)
training_p <- f2[ inTraining_p,]
testing_p  <- f2[-inTraining_p,]


fitControl <- trainControl(method="repeatedcv",
                            number=10, 
                              repeats=3,
                                sampling = "rose")

rf_ROSE <- train(as.factor(samesource) ~ ccf
                                        + rough_cor
                                        + D
                                        + sd_D
                                        + matches
                                        + mismatches
                                        + cms + non_cms
                                        + sum_peaks
                                        + overlap,
                  data = training_p,
                  method = "rf",
                  #preProcess = c("scale", "center"),
                  trControl = fitControl)
print(rf_ROSE)

rf_pred_ROSE <- predict(rf_ROSE, testing_p)
confusionMatrix(rf_pred_ROSE, as.factor(testing_p$samesource))

```

```{r}

set.seed(20140501)#20140501
inTraining_p <- createDataPartition(f2$samesource, p = .80, list = FALSE)
training_p <- f2[ inTraining_p,]
testing_p  <- f2[-inTraining_p,]


fitControl <- trainControl(method="repeatedcv",
                            number=10, 
                              repeats=3,
                                sampling = "smote")

rf_SMOTE <- train(as.factor(samesource) ~ ccf
                                        + rough_cor
                                        + D
                                        + sd_D
                                        + matches
                                        + mismatches
                                        + cms + non_cms
                                        + sum_peaks
                                        + overlap,
                  data = training_p,
                  method = "rf",
                  #preProcess = c("scale", "center"),
                  trControl = fitControl)
print(rf_SMOTE)

rf_pred_SMOTE <- predict(rf_SMOTE, testing_p)
confusionMatrix(rf_pred_SMOTE, as.factor(testing_p$samesource))

```

```{r}

All_Models <- list(No_Overlap = model_1,
               With_Overlap = model_2,
               Different_Seed = model_3,
               grid = rf_gridsearch,
               under = rf_under,
               over = rf_over,
               rose = rf_ROSE,
               smote = rf_SMOTE
               )




re <- resamples(All_Models)
bwplot(re)



```